```{r setup, include=FALSE}
library(ggplot2)
```

Import, Plot, Summarize, and Save Data

Using the Bureau of Labor Statistics data, choose a dataset that interest you. Load in the dataset from csv file.

Removed rows with NA data.

```{r}
coffee1 <- read.csv(file = "AvgCoffee.csv", header = TRUE)
coffee <- na.omit(coffee1)
```

Summary of dataset

```{r}
summary(coffee)
```

Generate summary statistics for 2 variables:

Summary of the January column within the dataset

```{r}
summary(coffee$Jan)
```

Summary of the February column within the dataset

```{r}
summary(coffee$Feb)
```

Plot some of the features (e.g., histograms, box plots, density plots, etc.) of several variables

Boxplot of January/Year

```{r}
janbox <- ggplot(coffee, aes(Year, Jan))
janbox + geom_boxplot() + labs(x="Year", y= "Jan")

```

Density of February

```{r}
jandensity <- ggplot(coffee, aes(Feb))
jandensity + geom_density() + labs(x="Feb", y = "Density")

```

Explore Some Bivariate Relations

Use the same dataset within the same website to explore some bivariate relations

Pearson correlation between all variables

```{r}
cor(coffee, use = "complete.obs", method = "pearson")
```

Pearson correlation between January and February

```{r}
cor(coffee$Jan, coffee$Feb, use = "complete.obs", method = "pearson")
```

Pearson correlation between March and April

```{r}
cor(coffee$Mar, coffee$Apr, use = "complete.obs", method = "pearson")
```

Scatterplot of January and February data

```{r}
coffeescatter <- ggplot(coffee, aes(Jan, Feb))
coffeescatter + geom_point() + geom_smooth(method = "lm", colour = "Blue") +labs(x="January", y= "February")
```

Scatterplot of March and April data

```{r}
coffeescatter <- ggplot(coffee, aes(Mar, Apr))
coffeescatter + geom_point() + geom_smooth(method = "lm", colour = "Red") +labs(x="March", y= "April")
```

Line Chart for January

```{r}
ggplot(coffee, aes(x = Year, y = Jan)) + geom_line() 
```

Line Chart for December

```{r}
ggplot(coffee, aes(x = Year, y = Dec)) + geom_line() 
```

Organize a Data Report

Summary of dataset

```{r}
summary(coffee)
```

Description of dataset
Average Prie of Coffee per lb, 100% ground roast

```{r}
str(coffee)
```
